\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-08 metatheory-condensed.tex
columnize

Derived families can be modeled as linkage transformers inductively
constructed from the introduction forms
$\InhId$, $\InhExt{h}{t}$, $\InhOv{h}{t}$, $\InhInh{h}$, etc.
\cref{fig:fmltt-selected} shows the beta rule of an exemplary transformer,
\ruleref{tmeq/ov/beta}.
It can be read as follows: given a linkage of form $\LkgAdd{\lkg}{t_1}$,
applying the transformer $\InhOv{h}{t_2}$ overrides the linkage's last
field~$t_1$ with~$t_2$.
For instance, the construction below shows that 
$\InhOv{\InhId}{\wcode{\wsig'_{\texttt{tm}}}}$ is used as the first step
in creating a derived family that
overrides $\wsig_{\texttt{tm}}$ with an extended
signature~$\wsig'_{\texttt{tm}}$.
\vspace{.9ex}

>>>>

Derived families can be modeled as linkage transformers inductively
constructed from the introduction forms
$\small\InhId$, $\small\InhExt{h}{t}$, $\small\InhOv{h}{t}$, $\small\InhInh{h}$, etc.
\cref{fig:fmltt-selected} shows the $\beta$-rule of an exemplary transformer,
\ruleref{tmeq/ov/beta}.
It states that applying the transformer $\small\InhOv{h}{t_2}$ to
a linkage of form $\LkgAdd{\lkg}{t_1}$
overrides the linkage's last field~$t_1$ with~$t_2$.
For instance, the construction below shows that 
$\small\InhOv{\InhId}{\wcode{\wsig'_{\texttt{tm}}}}$
is used as the first step in creating a linkage transformer modeling a derived family that
overrides $\wsig_{\texttt{tm}}$ with an extended
signature~$\wsig'_{\texttt{tm}}$.
\vspace{.9ex}
